Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
restructure sec. background

\section{Background: Cast Calculi} \label{sec:blame-calculus}

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2} \mid
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3} \mid
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOtt{} \mid
		\vOOfun{\rho}{x}{e} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

Now let's move to the dynamic semantics.

\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

@@

	\caption{Syntax of CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} 
	cast calculus}
\label{machine-cekc-syntax}
\end{figure}

@@

	\end{array}
	\]

%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s $}\\

@@

	\caption{Reduction rules of CEK abstract machine ($ \mathcal{D} $) for the 
	\lazyD{} cast calculus}
	\label{machine-cekc-reduction}
\end{figure}

Fig.~\ref{machine-cekc-syntax} defines the syntax of a CEK machine 
\citep{felleisen1986control} evaluating 
the \lazyD{} cast calculus.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy
\\---\\
Could you tell me why taking the value first is better?
I am always taking the target of induction/match first. -KC}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

@@

@@

  Syntax
  \[
  \begin{array}{rclr}
    \stxrule{v}{values}{
      \cdots \mid 
      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
      \vOOcast{v}{ \cOOcast{P}{l}{P} }
    }
  \end{array}
  \]

  \fbox{$\mathit{applyCast}(v,c) = r$}
  \[
  \begin{array}{rclr}
    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& v \\
    \mathit{applyCast}(v, \cOOcast{P}{l}{\star}) &=&
        v \langle \cOOcast{P}{l}{I} \rangle
          \langle \cOOcast{I}{l}{\star} \rangle
        & \text{if } I \sim P, I \neq P \\  
    \mathit{applyCast}(v, \cOOcast{\star}{l}{P}) &=&          
        v \langle \cOOcast{\star}{l}{I} \rangle
          \langle \cOOcast{I}{l}{P} \rangle
        & \text{if } I \sim P, I \neq P \\  
  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& v \\
  \mathit{applyCast}(v \langle \cOOcast{I_1}{l}{\star} \rangle , \cOOcast{\star}{l}{I_2}) &=& \rOOfail{l} & \text{if } I_1 \neq I_2 \\
  \mathit{applyCast}(v, \cOOcast{P_1}{l}{P_2}) &=&
     v \langle \cOOcast{P_1}{l}{P_2} \rangle & \text{if } P_1 \smile P_2
  \end{array}
  \]

>>>>

\section{Background} \label{sec:blame-calculus}

In this section, we review lazy cast calculi (\ref{sec:cast-calculi}) and
normal coercion (\ref{sec:coercion-calculus}).

\subsection{Cast Calculi}
\label{sec:cast-calculi}
\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2} \mid
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3} \mid
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOtt{} \mid
		\vOOfun{\rho}{x}{e} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -Jeremy
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

	\stxrule{\kappa}{continuations}{
		\mathtt{stop} \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa \mid
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
	}
	\stxrulecont{	
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
		\langle c \rangle \kappa
	}
	\end{array}
	\]
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}

@@

@@

	%	Transitive closure of reduction \fbox{$ s \longrightarrow_{D,B}^{*} s 
	%$}\\

@@

	\caption{dynamic semantics of the cast calculi as a CEK machine}
	\label{machine-cekc}
\end{figure}

Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
CEK machine \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
	machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -Jeremy
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction/match first. -KC}

@@

	\end{array}
	\]
	\caption{Definition of $ applyCast $ for \lazyD}
\end{figure}

We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

@@

\begin{figure}
%
%  Syntax
%  \[
%  \begin{array}{rclr}
%    \stxrule{v}{values}{
%      \cdots \mid 
%      \vOOcast{v}{ \cOOcast{I}{l}{\star} } \mid
%      \vOOcast{v}{ \cOOcast{P}{l}{P} }
%    }
%  \end{array}
%  \]
%  
  \fbox{$\mathit{applyCast}(v,c) = r$}
  \[
  \begin{array}{rclr}
    \mathit{applyCast}(v, \cOOcast{\star}{l}{\star} ) &=& v \\
    \mathit{applyCast}(v, \cOOcast{P}{l}{\star}) &=&
        v \langle \cOOcast{P}{l}{I} \rangle
          \langle \cOOcast{I}{l}{\star} \rangle
        & \text{if } I \sim P, I \neq P \\  
    \mathit{applyCast}(v, \cOOcast{\star}{l}{P}) &=&          
        v \langle \cOOcast{\star}{l}{I} \rangle
          \langle \cOOcast{I}{l}{P} \rangle
        & \text{if } I \sim P, I \neq P \\  
  \mathit{applyCast}(v \langle \cOOcast{I}{l}{\star} \rangle , \cOOcast{\star}{l}{I}) &=& v \\
  \mathit{applyCast}(v \langle \cOOcast{I_1}{l}{\star} \rangle , \cOOcast{\star}{l}{I_2}) &=& \rOOfail{l} & \text{if } I_1 \neq I_2 \\
  \mathit{applyCast}(v, \cOOcast{P_1}{l}{P_2}) &=&
     v \langle \cOOcast{P_1}{l}{P_2} \rangle & \text{if } P_1 \smile P_2
  \end{array}
  \]
